Sparse Function-space Representation \\ of Neural Networks

### 2023-05-15 paper/main.tex
Minor
Sec. 3

The contributions of this paper are:
%
{\em (i)}~We introduce \our, a new approach for sparse representation of the neural network in the function space.
{\em (ii)}~We demonstrate that, despite its sparsity, our method effectively captures predictive uncertainty, provides means of updating the model post-training, and gives a a compact representation suitable for continual learning.
{\em (iii)}~We provide extensive experiments for showcasing our approach and demonstrate significance and applicability across supervised, continual, and reinforcement learning, aiming to stimulate future use of the approach.

@@

\section{\our: Sparse Function-space Represenation of neural networks}
\paragraph{GP in the dual parameters}
As stated in \citet[Parameterization Lemma~1]{csato2002sparse}, the mean and covariance functions of the posterior process $f_{\textrm{post}}$, found through the Bayesian update using the GP prior and the likelihood function, can be parameterized by the dual parameters, $\valpha$ and $\vbeta$,
\begin{equation}  \label{eq:gp_pred}
  \myexpect_{p(f_i \mid\vy)}[f_i]= \vk_{\vx i}^\top \valpha \quad \text{and} \quad
  \mathrm{Var}_{p(f_i \mid \vy)}[f_i] = \kappa_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
\end{equation}
where the $ij$th entry of the matrix $\MKxx \in \R^{n \times n}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$th element is $\kappa(\vx_i, \vx_j)$, and $\kappa_{ii} = \kappa(\vx_i, \vx_i)$.  The dual parameters are the vector $\valpha \in \R^{m}$ and vector $\vbeta \in \R^{m}$, defined as:
\begin{equation}
\label{eq:dual_param}
\alpha_i \coloneqq \myexpect_{p(\vw \mid \vy)}[\nabla_{f_i}\log p(y_i \mid f_i)],  \quad
\beta_i \coloneqq - \myexpect_{p(\vw \mid \vy)}[\nabla^2_{f_i f_i}\log p(y_i \mid f_i)] .
\end{equation}
%
The above relations hold for generic likelihoods, and no approximations are involved as the expectation is under the exact posterior. 
It also highlights that our approximate inference technique, while usually considered a posterior approximation, can instead be seen as approximating the expectation of gradients of loss/likelihoods. \todo{our approximation is late \cref{eq:dual_param_laplace}, saying this here is misleading}\\
In \citet{csato2002sparse}, they iteratively find dual variables using an Expectation Propogation (EP) method.  
At the same time, in \cite{adam2021dual, chang2020fast}, they show this relationship for variational Gaussian processes where the above expectation is with respect to the approximate variational posterior. The dual parameter $\valpha$ appears also in non-Bayesian approaches, \eg, support vector machines \citep{cortes1995support}, whose origins are found in work by \citet{kimeldorf1971some}. While in \citet{wilkinson2023bayes}, they show links between linearization methods and how they solve the \cref{eq:dual_param}.\todo{is this last part used/referred somewhere else?}

>>>>

The contributions of this paper are:
%
{\em (i)}~We introduce \our, a new approach for sparse functional representation of the neural network.
{\em (ii)}~We demonstrate that, despite its sparsity, our method effectively captures predictive uncertainty, provides means of updating the model post-training, and gives a a compact representation suitable for continual learning.
{\em (iii)}~We provide extensive experiments for showcasing our approach and demonstrate significance and applicability across supervised, continual, and reinforcement learning, aiming to stimulate future use of the approach.

@@

\section{\our: Sparse function-space represenation of neural networks}
%\paragraph{GP in the dual parameters}
The early work by \citet{csato2002sparse} (Parameterization Lemma~1) states that the mean and covariance functions of the posterior process $f_{\textrm{post}}$, found through the Bayesian update using the GP prior and the likelihood function, can be parameterized by `dual' parameters, $\valpha$ and $\vbeta$,
%
\begin{equation}  \label{eq:gp_pred}
  \myexpect_{p(f_i \mid\vy)}[f_i]= \vk_{\vx i}^\top \valpha \quad \text{and} \quad
  \mathrm{Var}_{p(f_i \mid \vy)}[f_i] = k_{ii} - \vk_{\vx i}^\top ( \MKxx + \diag(\vbeta)^{-1})^{-1} \vk_{\vx i},
\end{equation}
%
where the $ij$\textsuperscript{th} entry of the matrix $\MKxx \in \R^{n \times n}$ is $\kappa(\vx_i,\vx_j)$, $\vk_{\vx i}$ denotes a vector where each $j$\textsuperscript{th} element is $\kappa(\vx_i, \vx_j)$, and $k_{ii} = \kappa(\vx_i, \vx_i)$.  The dual parameters are the vector $\valpha \in \R^{m}$ and vector $\vbeta \in \R^{m}$, defined as:
\begin{equation}
\label{eq:dual_param}
\alpha_i \coloneqq \myexpect_{p(\vw \mid \vy)}[\nabla_{f_i}\log p(y_i \mid f_i)],  \quad
\beta_i \coloneqq - \myexpect_{p(\vw \mid \vy)}[\nabla^2_{f_i f_i}\log p(y_i \mid f_i)] .
\end{equation}
%
The above relations hold for generic likelihoods, and no approximations are involved as the expectation is under the exact posterior. 
It also highlights that our approximate inference technique, while usually considered a posterior approximation, can instead be seen as approximating the expectation of gradients of loss/likelihoods. \todo{our approximation is late \cref{eq:dual_param_laplace}, saying this here is misleading}\\
In \citet{csato2002sparse}, they iteratively find dual variables using an Expectation Propogation (EP) method.  
At the same time, in \cite{adam2021dual, chang2020fast}, they show this relationship for variational Gaussian processes where the above expectation is with respect to the approximate variational posterior. The dual parameter $\valpha$ appears also in non-Bayesian approaches, \eg, support vector machines \citep{cortes1995support}, whose origins are found in work by \citet{kimeldorf1971some}. While in \citet{wilkinson2023bayes}, they show links between linearization methods and how they solve the \cref{eq:dual_param}.\todo{is this last part used/referred somewhere else?}
